### 2011-12-22 docs/compilers/compilers.tex
add information regarding the IBM compilers

\subsection{Intel}

@@

\subsection{gfortran}

\subsection{PGI}

\subsection{PathScale}

@@

\subsection{Cray}

>>>>

%-----------------------------------------------------------------------------
\subsection{Cray}

%-----------------------------------------------------------------------------
\subsection{gfortran}

%-----------------------------------------------------------------------------
\subsection{IBM (xl* compilers)}

Recent versions of these compilers seem to work ok.  Some notes:
\begin{itemize}
\item You need to use {\tt xlf95}, not {\tt xlf90} to compile, since
  MAESTRO relies on the Fortran 95 feature that arrays are
  automatically deallocated when you leave a subroutine.

\item Many (all?) IBM machines have a different endian-ness than
  Intel-like chips.  \boxlib\ plotfiles store information used to
  dechipher the endian-ness of the data.  To do this properly on
  the IBM machines, you need to set the preprocessor flag {\tt BL\_AIX},
  which is interpretted by {\tt fabio\_c.c}.  This can be done for the
  IBM compilers by adding {\tt -Wp,-DBL\_AIX} to the {\tt CFLAGS} variable.

%-----------------------------------------------------------------------------
\subsection{Intel}

@@

%-----------------------------------------------------------------------------
\subsection{PathScale}

@@

%-----------------------------------------------------------------------------
\subsection{PGI}
